Examination of shapes! (homework exam)

### 2016-02-23 geometricAlgorithms/homeworkExam/homeworkExam.tex
improved the algorithm from assignment 1
1.b finished I think
some changes to exam?
probably final version of 2b... probably

\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
%TODO: should we find the side?

\begin{algorithmic}
	\Function{findxySilhouette}{$v_{start}, v_{current}, S_{result}$}
	\If{$v_{start}$ is equal to $v_{current}$} 
		\State \Return $S_{result}$
	\EndIf
	\State
	$v_{next} \gets Origin(Next(IncidentEdge(v_{current})))$
	\State
	\Return \Call{findxySilhoeutte}{
		$v_{start}, v_{next}, S_{result} \cup v_{current}$
	}
	\EndFunction
	\Function{findxySilAlgoirthm}{$v_{start}$}
	\Comment{Helper function to suffice the contract (init work)}
	\State \Return
	\Call{findxySilhoeutte}{
		$v_{start}, Origin(Next(IncidentEdge(v_{start}))), Seq(v_{start})$
	}
	\Comment{The $Seq$ just makes an arbitrary sequence with constand append time}
	\EndFunction
	\State 
\end{algorithmic}

@@

\section{Red and blue lines}
\subsection{The status structure}
A binary tree sorted on the x axis.
\subsection{Initialization}
\subsection{Distinguish the events and describe for each event how its handled}
\subsection{Analyze the time}
\section{Polygon cut}
\section{Diagonal polygon cut}
\end{empfile}
\end{document}

>>>>

\newpage
\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
%TODO: should we find the side?
%TODO: walk to the side of the silhoutte

\begin{algorithmic}
	\State
	\Comment{Helper function to suffice the contract (init work)}
	\Function{findxySilAlgoirthm}{$v_{start}$}
	\State
	\Comment{Find the border of the silloutte}
	\State
	$\vec{e}_{init} \gets IncidentEdge(\Call{findxyBorderFirstImprovment}{v_{start}})$
	\State
	\Comment{The $Seq$ just makes an arbitrary sequence with constand append time}
	\State \Return
	\Call{findxySilhoeutte}{
		$Origin(\vec{e}_{init}), \vec{e}_{init}, Seq(\vec{e}_{init})$
	}
	\EndFunction
	\State
	\Comment{Finds the xyBorder by maximizing X}
	\Function{findxyBorderFirstImprovement}{$v_{start}$}
		\State
		\Comment{The incident is used to check when we've traversed all edges}
		\State
		$\vec{e}_{incident} \gets IncidentEdge(v_{start})$
		\Repeat
			\State
			$\vec{e}_{next} \gets Next(Twin(\vec{e}_{incident}))$
			\State
			$v_{candidate} \gets Origin(Next(\vec{e}_{next}))$
			\If{$v_{candidate}$ has bigger x than $v_{start}$}
				\State
				\Comment{The return statment will break the loop}
				\State
				\Return \Call{findxyBorderFirstImprovement}{$v_{candidate}$}
			\EndIf
		\Until{$\vec{e}_{next}$ is not equal to $\vec{e}_{incident}$}
		\State
		\Comment{If the loop finds no improvment we've maximized X and are on the border}
		\State \Return $v_{start}$
	\EndFunction
	\Function{findxySilhouette}{$v_{start}, \vec{e}_{current}, S_{result}$}
	\State
	\Comment{Base case, passing the start all the way down doesn't require us to do marking}
	\If{$v_{start}$ is equal to $Origin(\vec{e}_{current})$}
		\State \Return $S_{result}$
	\EndIf
	\State
	\Comment{Figuring out which edge to do next}
	\State
	$\vec{e}_{next} \gets Next(\vec{e}_{current})$
	\State
	\Comment{We use another recursive funtion for this}
	\State
	$\vec{e}_{next} \gets \Call{findLeastRotatingEdge}{Twin(\vec{e}_{current}), Next(Twin(\vec{e}_{next})), \vec{e}_{next}}$
	\State
	\Return \Call{findxySilhoeutte}{
		$v_{start}, \vec{e}_{next}, S_{result} \cup \vec{e}_{current}$
	}
	\EndFunction
	\Function{findLeastRotatingEdge}{$\vec{e}_{start}, \vec{e}_{current}, \vec{e}_{best}$}

	\Comment{Trying to get an as shallow rotation as possible}
	\If{$\vec{e}_{current}$ rotation is bigger than $\vec{e}_{best}$ (with as orientation point $Prev(\vec{e}_{start})$)}
		\State
		$\vec{e}_{best} \gets \vec{e}_{current}$
	\EndIf
	\State
	\Comment{Base case for recursion}
	\If{$\vec{e}_{start}$ is equal to $\vec{e}_{current}$}
		\State
		\Return $\vec{e}_{best}$
	\EndIf
	\Comment{Going deeper because there is another step}
	\State
	\Return \Call{findLeastRotatingEdge}{$\vec{e}_{start},Next(Twin(\vec{e}_{current})),\vec{e}_{best}$}
	\EndFunction
	\State 
\end{algorithmic}

@@

\section{Red and blue lines}
\subsection{The status structure}
A binary tree sorted on the x axis.
\subsection{Initialization}

\subsection{Distinguish the events and describe for each event how its handled}
\subsection{Analyze the time}

\section{Polygon cut}
\section{Diagonal polygon cut}
\end{empfile}
\end{document}
